NYC Spatial Models - Comparison of Spatial Models With and Without Twitter Data

### 2019-12-11 NYC_Twitter_SDM_models - Copy.Rmd
extract the function `impacts_extractor`

```{r obese_sdm_age_impacts}
impacts_extractor <- function(sdm) {

  impacts_summary <- summary(impacts(sdm, tr=trMC, R=1000), zstats = TRUE)

  coef <- list(
    direct = impacts_summary$direct_sum,
    indirect = impacts_summary$indirect_sum,
    total = impacts_summary$total_sum
  ) %>%
  lapply(function(s) {
    data_frame(
      var = names(s$statistics[,1]),
      impact = s$statistics[,1]
    )
  }) %>%
    bind_rows(.id = "effect")

  pval <- as_data_frame(impacts_summary$pzmat) %>%
    mutate(
     var = rownames(impacts_summary$pzmat)
    ) %>%
    gather("effect", "p-val", -var) %>%
    mutate(effect = tolower(effect))

  left_join(coef, pval, by = c("effect", "var"))
}

>>>>

```{r obese_sdm_age_impacts}
